Childcare while their mom is working

### 2022-04-02 outputs/paper.Rmd
Small updates in table

```{r data, echo=FALSE}
ghana %>%
  select(background, no_child_under_six, one_more_child_under_six, caretaker_respondent, number_of_employed_women, character) %>%
  slice(5:6, 13:20, 26) %>%
  kable(caption='A subset of key features',
        col.names = c('Background', 'No child under six', '1+ child under six', 
                      'Child\'s caretaker- respondent', 'Number of employed women', 'Category'),
        digits = 1,
        booktabs = FALSE,
        linesep = "") %>%
  kable_styling(position = "center")
  add_footnote("Numbers are in percentage (%).")
```

>>>>

```{r data, echo=FALSE}
ghana %>%
  select(background, no_child_under_six, one_more_child_under_six, caretaker_respondent, number_of_employed_women, character) %>%
  relocate(no_child_under_six, .after = one_more_child_under_six) %>%
  slice(5:6, 13:20, 26) %>%
  kable(caption='A subset of key features',
        col.names = c('Background', 'Yes', 'No', 'Respondent', 'Number of employed women', 'Category'),
        digits = 1,
        booktabs = TRUE,
        linesep = "",
        align = c('l', 'c', 'c', 'c', 'c', 'l'),) %>%
  add_header_above(c(" " = 1, "Child under six" = 2, "Child's caretaker" = 1, " " = 2),
                   escape=F) %>%
  add_footnote("Decimals are in percentage (%).")
```
